final-project

### 2024-11-05 final-project.Rmd
clean data

# further filter and select only variables used in analysis
seer <- seer_clean %>%
  filter(
    !is.na(subtype)
  ) %>%
  select(
    age,
    sex,
    year_diagnosis,
    race,
    marriage_status,
    subtype,
    t_stage = tnm,
    n_stage,
    m_stage,
    grade,
    idc_type,
    radiation,
    chemotherapy,
    surgery,
    survival_months,
    survival_status,

>>>>

# further filter and select only variables used in analysis
seer <- seer_clean %>%
  filter(
    !is.na(subtype),
    !is.na(grade),
    n_stage != "NX"
  ) %>%
  select(
    age,
    sex,
    year_diagnosis,
    race,
    marriage_status,
    subtype,
    t_stage = tnm,
    n_stage,
    m_stage,
    grade,
    idc_type,
    radiation,
    chemotherapy,
    surgery,
    survival_months,
    survival_status,
